Title of the document here

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
removed abstract+duplicate text and moved table

\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top 
   of the left-hand column, below the author and affiliation 
   information. Use the word ``Abstract'' as the title, in 12-point 
   Times, boldface type, centered relative to the column, initially 
   capitalized. The abstract is to be in 10-point, single-spaced type. 
   The abstract may be up to 3 inches (7.62 cm) long. Leave two blank 
   lines after the Abstract, then begin the main text. 
\end{abstract}

@@

The purpose of this survey study is therefore to find what are the differences in readability between five common and well known programming languages. With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
\newline

The Independent variables will be defined as the experience, occupation, preferred language, least preferred language and the working language of the participant. The dependent variable in this example will be the readability of the language.
\newline

@@

\newline

@@

\SubSection{Results Analysis}
The response rate for the questionnaire was 11\%. The questionnaire was distributed to 270 members of the sample group and 29 members returned the survey. An additional 6 students have answered the questionnaire in a second iteration, where they were personally contacted based on which year they were attending. Table XXX1 displays information of the respondents experience level. Table XXX2 shows the year which the students are attending. 
\newline

@@

\begin{table}[ht]
  \centering
  \begin{tabular}{| l | r | c |}
  	\hline
  	\textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
  	Experience & RQ1, SQ1 & 1 \\ \hline
    Academic Year & RQ1, SQ1 & 2 \\ \hline
  	Preferred Language & RQ1, SQ2 & 3 \\ \hline
  	Least Preferred Language & RQ1, SQ2& 4 \\  \hline
  	Experience of Language & RQ1, SQ2 & 5 \\ 
  	\hline
	\end{tabular}
  \caption{ Hiadsdsafdsaf}
\end{table}

>>>>

@@

The independent variables will be defined as the experience, occupation, preferred language, least preferred language and the working language of the participant. The dependent variable in this example will be the readability of the language.
\newline

@@

@@

\begin{table}[ht]
  \centering
  \begin{tabular}{| l | r | c |}
    \hline
    \textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
    Experience & RQ1, SQ1 & 1 \\ \hline
    Academic Year & RQ1, SQ1 & 2 \\ \hline
    Preferred Language & RQ1, SQ2 & 3 \\ \hline
    Least Preferred Language & RQ1, SQ2& 4 \\  \hline
    Experience of Language & RQ1, SQ2 & 5 \\ 
    \hline
  \end{tabular}
  \caption{Independant variables' relation to Research Questions}
\end{table}

\SubSection{Results Analysis}
The response rate for the questionnaire was 11\%. The questionnaire was distributed to 270 members of the sample group and 29 members returned the survey. An additional 6 students have answered the questionnaire in a second iteration, where they were personally contacted based on which year they were attending. 
\newline

@@
